MRPSO: MapReduce Particle Swarm Optimization

### 2009-01-06 crystallography/paper.tex
Modified date on paper.tex, added a few papers
Started on the crystallography description

\conferenceinfo{GECCO'07,} {July 7--11, 2007, London, England.}
\CopyrightYear{2007}
%\crdata{1-59593-186-4/06/0007}

\title{MRPSO: MapReduce Particle Swarm Optimization}
\numberofauthors{3}
%\author{%
%\alignauthor Andrew McNabb\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Computer Science Dept.}\\
%    \affaddr{3361 TMCB, Provo, UT 84602}\\
%    \email{a@cs.byu.edu}
%\alignauthor Christopher Monson\\
%    \affaddr{Google, Inc.}\\
%    \affaddr{4720 Forbes Ave., Lower Level}\\
%    \affaddr{Pittsburgh, PA 15213}\\
%    \email{c@cs.byu.edu}
%\alignauthor Kevin Seppi\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Computer Science Dept.}\\
%    \affaddr{3361 TMCB, Provo, UT 84602}\\
%    \email{k@cs.byu.edu}
%}
\date{}

@@

\section*{Track Category}
FIXME. Ant Colony Optimization, Swarm Intelligence, and Artificial Immune Systems

@@

\section{Introduction}

@@

>>>>

\conferenceinfo{GECCO'09,} {July 8--12, 2009, Montr\'eal, Canada.}
\CopyrightYear{2009}
%\crdata{1-59593-186-4/06/0007}

\title{MRPSO: MapReduce Particle Swarm Optimization}
\numberofauthors{4}
%\author{%
%\alignauthor Matthew Gardner\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Computer Science Dept.}\\
%    \affaddr{3361 TMCB, Provo, UT 84602}\\
%    \email{mjg82@cs.byu.edu}
%\alignauthor Andrew McNabb\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Computer Science Dept.}\\
%    \affaddr{3361 TMCB, Provo, UT 84602}\\
%    \email{a@cs.byu.edu}
%\alignauthor Branton Campbell\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Physics Dept.}\\
%    \affaddr{N261 ESC, Provo, UT 84602}\\
%    \email{branton_campbell@byu.edu}
%\alignauthor Kevin Seppi\\
%    \affaddr{Brigham Young University}\\
%    \affaddr{Computer Science Dept.}\\
%    \affaddr{3361 TMCB, Provo, UT 84602}\\
%    \email{k@cs.byu.edu}
%}
\date{}

@@

\section*{Track Category}
FIXME. Ant Colony Optimization, Swarm Intelligence

@@

\section{Introduction}
\label{sec:intro}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Crystallography

\section{Crystallography}
\label{sec:crystallography}

FIXME.
TODO: Where to put the butterfly problem definition? Should I describe 
simulated annealing or gradient descent, at least briefly?

The point of crystallography is to determine the structure of a crystal.  This
is done by shining x-rays through the crystal and observing the patterns that
come out.  Those patterns are then compared to the output of a model of the 
crystal -- if the two match, the model can be considered correct.  The model
may consist of the positions of all of the atoms in the crystal, the 
distortion coefficients of the materials, the length and width of nanopolar
domains, or various other parameters.  The task of finding the parameters to 
the model that best fit the data is well suited to optimization techniques.  
The function to be optimized is an error function -- the average difference
between the model output and the data, for every data point.

There are commercial packages that readily solve some crystallography problems,
such as (ask Dr. Campbell), that uses simulated annealing for specific types 
of problems.  Gradient descent is also a commonly used method for solving these
problems.  Particle swarm optimization, however (to our knowledge?), has not 
been used.

We encountered a problem for which gradient descent proved uneffective.

To solve crystallography problems, one must fit the parameters of the model
to the data.  The more data is used, the more accurate the result will be, but
with large amounts of data the evaluation time can be inhibitively large.  In
our first attempts at solving this problem, the function evaluation took close
to an hour.  We then trimmed the amount of data we were using, and the time for
a function evaluation decreased to about four minutes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PSO
